---
title: "finalProject2_KanaparthiVenkata"
author: "Venkata Kanaparthi"
date: "5/23/2021"
output: pdf_document
---

```{r include=TRUE, echo=FALSE, message = FALSE, warning = FALSE}
library(ggm)
library(ggplot2)
library(readr)
library(pastecs)
library(readxl)
library(plyr)
library(dplyr)
library(magrittr)
library(purrr)
library(stringr)
library(QuantPsyc)
library(caTools)
library(survival)
```

## How to import and clean my data

Data Import

We can use read_csv() to import the data into a data frame
Ex: 
lendClubLoans_df <- read_csv("data/finalProject/Final_Project_LendingData.csv", stringsAsFactors = FALSE)

Data Cleaning

1.) Removed Duplicates
2.) Check for a person whether he has multiple loans are not. But did not find.

Fields that are retained from the original data set are which I feel can be utilized to predict the loan status

id	
member_id	
loan_amnt	
funded_amnt	
funded_amnt_inv	
term	
int_rate	
installment	
home_ownership	
annual_inc	
verification_status	
issue_d	
loan_status	
addr_state	
fico_range_low	
fico_range_high

## What does the final data set look like?
```{r include=TRUE,echo=FALSE, message = FALSE, warning = FALSE}
setwd('E:/MSDS-SEM2/DSC520/CodingAssignments/DSC520KANAPARTHI')
lendClubLoans_df <- read_csv("data/finalProject/Final_Project_LendingData.csv")
head(lendClubLoans_df)
```
## What information is not self-evident?
Data looks good. No Issue

## What are different ways you could look at this data?
1.) Interest Rate Vs Loan Status (Charged off or not)
2.) Annual Income Vs Loan Status (Charged off or not)

## How do you plan to slice and dice the data?
#Do you plan to slice and dice the data in different ways, create new variables, or join separate data frames to create new summary information? Explain.
We have multiple status of loans in the loan status field, would like to take only customers those were charged off into one variable and others into another variable of data frame type.

## How could you summarize your data to answer key questions?
We use summary() function on the model that is used which helps us in providing the R and Rsquared if Linear model and AIC, Deviations if it is a Logistic regression. It will provide us the information on how predictors influence the outcome

## What types of plots and tables will help you to illustrate the findings to your questions?
Scatter plots, histograms, line graphs

## Do you plan on incorporating any machine learning techniques to answer your research questions? Explain.
Would like to use logistic Regression on the data, As Charge off Yes or No(Categorical Variable) is the outcome based on the predictors (Continuous or Categorical variables).
